Non-coding RNAs of bird genomes

### 2013-07-29 paper/manuscript.tex
Updated Gallus annotations to galGal4.
Updated manuscript.

\author{
Paul P. Gardner\correspondingauthor$^{1,2}$
\email{Paul P. Gardner\correspondingauthor - paul.gardner@canterbury.ac.nz},
Sarah W. Burge$^3$
\email{sb30@sanger.ac.uk},
Maria Ninova$^4$
\email{Maria.Ninova@postgrad.manchester.ac.uk},
Stephanie Kehr$^5$
\email{steffi@bierdepot.bioinf.uni-leipzig.de},
Anne Nitsche$^5$
\email{anne@bierdepot.bioinf.uni-leipzig.de},
Mario Fasold$^5$
\email{mario@bierdepot.bioinf.uni-leipzig.de},
Tammy E. Steeves$^1$
\email{tammy.steeves@canterbury.ac.nz},
Sam Griffiths-Jones$^4$
\email{sam.griffiths-jones@manchester.ac.uk}
and
Peter Stadler\correspondingauthor$^5$
\email{Peter Stadler\correspondingauthor - studla@bioinf.uni-leipzig.de}
}
\address{
\iid(1) School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch, New Zealand.
\iid(2) Biomolecular Interaction Centre, University of Canterbury, Private Bag 4800, Christchurch, New Zealand.
\iid(3) European Molecular Biology Laboratory, European Bioinformatics Institute, Hinxton, Cambridge, CB10 1SD, UK.
\iid(4) Faculty of Life Sciences, University of Manchester, Manchester, United Kingdom.
\iid(5) Bioinformatics Group, Department of Computer Science; and Interdisciplinary Center for Bioinformatics, University of Leipzig, Härtelstrasse 16-18, D-04107 Leipzig, Germany
}

@@

%% Paul P. Gardner1,2, Sarah W. Burge3, Jana Hertel5, Maria Ninova4, Stephanie Kehr5, Anne Nitsche5, Mario Fasold5, Tammy E. Steeves1, Sam Griths-Jones4, Peter Stadler5

@@

%% Talking points:
%% 1.     Although the majority of classical eukaryotic ncRNAs are conserved in birds, several notable classical ncRNAs are not. Homology searches in associated genes indicate these apparent "losses" are most likely due to divergence.
%% 2.     Of the 59 snoRNA conserved between humans and yeast, we find 45 are conserved in birds. Homology searches in associated genes for the remaining non-conserved snoRNAs indicate these apparent losses are indeed due to multiple losses in several bird lineages.
%% 3.     We find several miRNA families are specific to the avian lineage.

@@

%%%%%LNCRNA:

@@

@@

The Vault RNA forms a major component of the vault ribonucleoprotein
complex, this is one of the largest particles found in the vertebrate
cell; In fact, it is larger than the ribosome \cite{Kong:1999}. As yet
not much is known about the function of Vault. The Vault RNA has been
shown to be broadly conserved in metazoans \cite{Stadler:2009}.

>>>>

\author{
Paul P. Gardner\correspondingauthor$^{1,2}$
\email{Paul P. Gardner\correspondingauthor - paul.gardner@canterbury.ac.nz},
Jana Hertel$^5$
\email{Jana Hertel\correspondingauthor - jana@bioinf.uni-leipzig.de},
Sarah W. Burge$^3$
\email{sb30@sanger.ac.uk},
Maria Ninova$^4$
\email{Maria.Ninova@postgrad.manchester.ac.uk},
Stephanie Kehr$^5$
\email{steffi@bierdepot.bioinf.uni-leipzig.de},
Mario Fasold$^5$
\email{mario@bierdepot.bioinf.uni-leipzig.de},
Tammy E. Steeves$^1$
\email{tammy.steeves@canterbury.ac.nz},
Sam Griffiths-Jones$^4$
\email{sam.griffiths-jones@manchester.ac.uk}
and
Peter Stadler\correspondingauthor$^5$
\email{Peter Stadler\correspondingauthor - studla@bioinf.uni-leipzig.de}
}
\address{
\iid(1) School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch, New Zealand.
\iid(2) Biomolecular Interaction Centre, University of Canterbury, Private Bag 4800, Christchurch, New Zealand.
\iid(3) European Molecular Biology Laboratory, European Bioinformatics Institute, Hinxton, Cambridge, CB10 1SD, UK.
\iid(4) Faculty of Life Sciences, University of Manchester, Manchester, United Kingdom.
\iid(5) Bioinformatics Group, Department of Computer Science; and Interdisciplinary Center for Bioinformatics, University of Leipzig, Härtelstrasse 16-18, D-04107 Leipzig, Germany
}

@@

%% Paul P. Gardner1,2, Sarah W. Burge3, Jana Hertel5, Maria Ninova4, Stephanie Kehr5, Anne Nitsche5, Mario Fasold5, Tammy E. Steeves1, Sam Griffiths-Jones4, Peter Stadler5

@@

%% Talking points:
%% 1.     Although the majority of classical eukaryotic ncRNAs are conserved in birds, several notable classical ncRNAs are not. Homology searches in associated genes indicate these apparent "losses" are most likely due to divergence.
%% 2.     Of the 59 snoRNA conserved between humans and yeast, we find 45 are conserved in birds. Homology searches in associated genes for the remaining non-conserved snoRNAs indicate these apparent losses are indeed due to multiple losses in several bird lineages.
%% 3.     We find that 3 families of broadly conserved vertebrate microRNA families are lost in the avian lineage.  We also annotate a number of bird-specific microRNAs.

@@

%% LNCRNA:

@@

%Furthermore our results contradict the text in the paper. We find
%SNORD26 stated to be lost in sauropsids in the 5 species:
%C.vociferus, M.unicolor, H.leucocephalus, L.discolor and T.guttata.

@@

The Vault RNA forms a major component of the vault ribonucleoprotein
complex, this is one of the largest particles found in the vertebrate
cell; In fact, it is larger than the ribosome \cite{Kong:1999}. As yet
not much is known about the function of Vault. The Vault RNA has been
shown to be broadly conserved in metazoans
\cite{Stadler:2009}. However, in the bird lineages
